New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/schur.tex
petit oubli

Using a SAT solver, we exhibited SF-templates, hence providing lower bound on \(S^+\) and inequalities 
of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5, we looked for symmetric SF-templates, 
we assumed that the special color was the last color to appear and we constrained the \(m_c\)'s out of being too small.

>>>>

Using a SAT solver, we exhibited SF-templates, hence providing lower bound on \(S^+\) and inequalities 
of the type \(S(n+k) \geqslant a S(n) + b\). We have sought templates providing the greatest value of 
\((a, b)\) (for the lexicographic order). When the number of colors excceeded 5,in order to reduce the search space we 
looked for symmetric SF-templates, we assumed that the special color was the last color to appear and we constrained 
the \(m_c\)'s out of being too small. Further details about the encoding as a SAT problem can be found in the
\hyperref[SAT]{SAT section}. \\
